### 2017-01-20 R/ITHIM.Rmd
Save the rds ITHIM object for national run
Small tweak to ITHIM.Rmd

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("knitr","ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
install("~/ITHIM/")
#install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = FALSE}
document("~/ITHIM/")
#install("~/ITHIM/")
install_github("syounkin/ITHIM", ref="devel")
install_github("smbache/magrittr", ref="master")

@@

saveRDS(ITHIM.national, file = "./data/ITHIM.national.rds")
